Nesta attacks study

### 2021-08-11 paperDraft/paperDraft.Rmd
started work on experimental design

#Collective Intelligence Approach

#Experimental Design

#Results

>>>>

# Collective Intelligence Approach to Counter-speech

# Experimental Design
This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
We formed treatment and control groups based on three main criteria:
1. During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily. Thus, we needed approximately 200 attacks daily generated by the treatment groups.
2. Recruitment of users who regularly attack others was necessary to measure the effect of interventions at the end.
3. Recruitment of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
First, we spent 9 weeks for preliminary Reddit's monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring. As mentioned, sustained activity was crucial to minimize the risk users becoming inactive during the course of the study. Next, we have calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day - 1.94 attacks daily per person on average). Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per group). The rest (304 people) were selected as our control group.

Three groups were formed - two treatment groups (195 people in each) and one control group (304 people). The first treatment group received counter-speech interventions based on normative influence, while the second one received interventions based on empathetic influence. Users in the control group did not receive any intervention.

The duration of the experiment, 6 months, was divided into three 2-months periods. The first two months served as a monitoring period to properly select groups and establish baselines. The next 2 months served as treatment period, during which groups received counter-speech comments from volunteers, in response to personal attacks detected by the Artificial Intelligence-based system. The last 2-months served as the post-treatment monitoring period to gather the data needed to evaluate the effectiveness of interventions.

Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others.
E.g. Insulting others is against Reddit's policy. 
Hey there, we do not call each other like that here.
Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both. They are designed to evoke an empathetic response. 
E.g. There is a human being on the other side who might be hurt by your words.
I see you are frustrated but remember the human.

Cyberviolence was defined in this experiment as a personal attack - any kind of verbal harassment, insult, or threat directed against the interlocutor in a text-based conversation online. Those were detected using Samurai Labs' cyberviolence detection system.

The following hypotheses were formulated:

H1: If a group of human volunteers notified by an AI-based cyberviolence detection system about cyberviolence generated by the treatment group users (cyberviolence will be defined as a personal attack, harassment, or a threat targeted against an interlocutor) responds with counter-speech interventions, this will result in a decreased cyberviolence level for the whole group after the intervention period.

H2: If two groups receive different types of interventions (empathy-based or normative), then the decrease in cyberviolence will be larger in the case of normative interventions in comparison to the empathy-based ones.

# Results

### 2021-08-11 paperDraft/paperDraft.tex
started work on experimental design

\#Collective Intelligence Approach

\#Experimental Design

\#Results

>>>>

\hypertarget{collective-intelligence-approach-to-counter-speech}{%
\section{Collective Intelligence Approach to
Counter-speech}\label{collective-intelligence-approach-to-counter-speech}}

\hypertarget{experimental-design}{%
\section{Experimental Design}\label{experimental-design}}

This was a 6-months field experiment in a digital setting conducted on a
popular Q\&A and news forum, Reddit (www.reddit.com). We formed
treatment and control groups based on three main criteria: 1. During the
intervention period, we have expected to have 20 active volunteers at
any given time, each willing to conduct 10 interventions daily. Thus, we
needed approximately 200 attacks daily generated by the treatment
groups. 2. Recruitment of users who regularly attack others was
necessary to measure the effect of interventions at the end. 3.
Recruitment of users who were active during the whole preliminary
monitoring period was necessary to minimize the risk of attrition during
the study. First, we spent 9 weeks for preliminary Reddit's monitoring
period to recruit only those users who generate at least one personal
attack per week and were active during the whole period of the
monitoring. As mentioned, sustained activity was crucial to minimize the
risk users becoming inactive during the course of the study. Next, we
have calculated the daily average number of personal attacks generated
by the group who met the above criteria (which resulted in 357 attacks
per day - 1.94 attacks daily per person on average). Knowing that we
need around 200 attacks daily (just enough so our volunteers can keep up
with the volume) we have randomly selected 390 people for our study
groups (195 per group). The rest (304 people) were selected as our
control group.

Three groups were formed - two treatment groups (195 people in each) and
one control group (304 people). The first treatment group received
counter-speech interventions based on normative influence, while the
second one received interventions based on empathetic influence. Users
in the control group did not receive any intervention.

The duration of the experiment, 6 months, was divided into three
2-months periods. The first two months served as a monitoring period to
properly select groups and establish baselines. The next 2 months served
as treatment period, during which groups received counter-speech
comments from volunteers, in response to personal attacks detected by
the Artificial Intelligence-based system. The last 2-months served as
the post-treatment monitoring period to gather the data needed to
evaluate the effectiveness of interventions.

Normative interventions can refer either to general social norms of
civility and respect, community standards, a particular subreddit rule,
or a descriptive norm among others. E.g. Insulting others is against
Reddit's policy. Hey there, we do not call each other like that here.
Empathetic interventions can refer to the emotional state of the
recipient or the sender of the attack or both. They are designed to
evoke an empathetic response. E.g. There is a human being on the other
side who might be hurt by your words. I see you are frustrated but
remember the human.

Cyberviolence was defined in this experiment as a personal attack - any
kind of verbal harassment, insult, or threat directed against the
interlocutor in a text-based conversation online. Those were detected
using Samurai Labs' cyberviolence detection system.

The following hypotheses were formulated:

H1: If a group of human volunteers notified by an AI-based cyberviolence
detection system about cyberviolence generated by the treatment group
users (cyberviolence will be defined as a personal attack, harassment,
or a threat targeted against an interlocutor) responds with
counter-speech interventions, this will result in a decreased
cyberviolence level for the whole group after the intervention period.

H2: If two groups receive different types of interventions
(empathy-based or normative), then the decrease in cyberviolence will be
larger in the case of normative interventions in comparison to the
empathy-based ones.

\hypertarget{results}{%
\section{Results}\label{results}}
